Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-04-08 ms.tex
blah

    \item We adopt halo average star formation rates measured in
      cosmological simulations by \citet{MosterNaab+:2013a}, and
      neglect any spatial variation in the star formation rate for any
      given galaxy. Galaxies with masses$\gsim 7\times 10^{10} \Msun$,
      assemble their stars from the inside out
      \citet{PerezCidFernandes+:2013a}
      and so for a given halo mass
      the galactic nucleus may be significantly older than in our
      model and thus more prone to thermal instability.

>>>>

    \item We adopt halo average star formation rates measured in
      cosmological simulations by \citet{MosterNaab+:2013a}, and
      neglect any spatial variation in the star formation rate for any
      given galaxy. Galaxies with masses$\gsim 7\times 10^{10} \Msun$,
      assemble their stars from the inside out
      \citep{PerezCidFernandes+:2013a}
      and so for a given halo mass
      the galactic nucleus may be significantly older than in our
      model and thus more prone to thermal instability.
